Bathtub Qualitative Reasoning

### 2016-10-21 paper.tex
trolololo

>>>>

The trace reports how the algorithm expands the state graph and how it determines all the possible transitions for a state.

In particular the trace gives insights on the procedure for computing the possible successors. It shows how the values are assigned and how the constraints are propagated. It also tells when we discard a partial assignment because it violates value or continuity constraints.

However we decided to show the big picture of what the algorithm is doing than to print every single step in order keep the file readable. Thus we don't report all the intermediate steps and computations the programs is performing highlighting only the principal steps.
